Interactive Visual Analysis of Lumbar Back Pain \subtitle{What the Lumbar Spine Tells About Your Life}

### 2014-12-12 draft.tex
added correct classification metric description

The error is scaled to denote perfect classification with 0; 1 is equal to random selection.

@@

We consider a result rated $0.5$ or below good enough to display it in the visualization, a value below $0.25$ represents a good classification.

>>>>

%The error is scaled to denote perfect classification with 0; 1 equals always wrong; 0.5 equals random selection.
The error represents the share of incorrect classifications and denotes perfect classification with 0; always wrong with 1; and random selection with 0.5.

@@

We display results below $0.5$ in the visualization, a value below $0.25$ represents a good classification.
%We consider a result rated  or below good enough to display it in the visualization, a value below $0.25$ represents a good classification.
